ChIPexo QC figures

### 2015-10-29 rmarkdown/ChIPexo_QC_figures_list.Rmd
Added scripts to work with the old aerobic exponential ChIPexo Sig70 data

    a. Diagram of how the pipeline works, rough explanation of biases and effects that are being measured
    b. Comparison of all datasets under current quality measures and comparison with the measures for the respective chipseq datasets. For the case of strand cross correlation it may be necessary to emphasize the absence of input reads for chipexo, which makes measures as RSC and NSC unavailable.

@@

I haven't paid to much attention to this, are we going to make comparisons with more datasets or only use the one that we have ?

>>>>

    a. Diagram of how the pipeline works, rough explanation of biases and effects that are being measured

        a1. The diagram may consist of 3 parts: Coverage plot, vector of stats per island, summary measures

    b. Comparison of all datasets under current quality measures and comparison with the measures for the respective chipseq datasets. For the case of strand cross correlation it may be necessary to emphasize the absence of input reads for chipexo, which makes measures as RSC and NSC unavailable.

@@

1. Since we only published this comparison for ChIPseq PET and SET, it is gonna be necessary to make comparisons of ChIPexo. We already have the one speaking about resolution, but it may be worth look at different measures.
